% Copyright 2012 Oz Nahum Tiram <nahumoz@gmail.com>
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.

\documentclass[a4papper,overlapped,line]{res}
% \documentclass[a4papper,margin,line]{res}
\newsectionwidth{.7cm}
\usepackage{color}
\definecolor{SOrange}{rgb}{1,0.44,0.04}

\usepackage{scalefnt}

\usepackage{tikz}
\newcommand{\mytag}[1]{
\begin{tikzpicture}[baseline={(TAG.base)}]
  \node[draw, minimum height=1ex] (TAG) {#1};
\end{tikzpicture}}


\usetikzlibrary{shapes.geometric}
\newcommand{\tagf}[2][]{
{
\scalefont{0.8}
\begin{tikzpicture}[baseline={(TAG.base)}]
\node[draw,#1] (TAG) {#2\strut};
\end{tikzpicture}
}
}

\tikzset{My Tag Style/.style={blue!80, 
         fill=blue!20,  
         rounded corners}}

\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage{times} 
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newcommand{\jobdes}[3]{{\bf \large #1\hspace{2ex}}{{\em \small #2}}{\hfill #3}}
%use like \jobdes{job title}{company, location}{dates}

\newcommand{\osection}[1]{\section{\sc {\color{SOrange}\vspace{-0.60cm} \textbf{#1}\\}}}

\usepackage{changepage}

\newenvironment{changemargin}[2]{\begin{list}{}{
\setlength{\topsep}{0pt}\setlength{\leftmargin}{0pt}
 \setlength{\rightmargin}{0pt}
 \setlength{\listparindent}{\parindent}
 \setlength{\itemindent}{\parindent}
 \setlength{\parsep}{0pt plus 1pt}
 \addtolength{\leftmargin}{#1}\addtolength{\rightmargin}{#2}
 }\item }{\end{list}}



\begin{document}

\name{{\color{SOrange}Oz Nahum Tiram, M.Sc. }} 

% To change the name size change 
% \def\namefont{\large\bf} to for example
% \def\namefont{\Large\bf}

\address{ \begin{tabular}{ll}
xxxxxxstr. 10            & {\it Land-line:}  +49 891 xxxxxx \\            
8xx37 München & {\it Mobile:}                +49 176 xxxxx294 \\         
 & {\it E-mail:}  nahumoz@gmail.com\\       
 & {\it WWW:} linuxpixies.blogspot.com\\ 
 &\hspace{2.7em}             \\     
\end{tabular}}

% for a simple format
% \address{+1 321 223 2223 || jackie@tran.com}
% \address{Someville, Someland }

\begin{resume}

% \vspace{0.60cm}

\begin{changemargin}{-0.7cm}{-2.3cm}
{\setlength{\fboxsep}{18pt}
\colorbox{blue!20}{
\begin{minipage}{0.95\textwidth}

\rmfamily
%\ttfamily
\begin{flushleft}
\hspace{-0.54cm}{\scalefont{1.2}\textbf{\begin{Huge}\textquotedblleft\end{Huge}}}
\\
\vspace{-0.65cm}
\begin{small}
I strive to solve interesting problems. I like to find solutions which don't hunt you down two months later, 
because you wanted some patchy solution that just works. That's exactly why I 
wanted to start programming and why I use Linux. For me programming started as a way to process my data and
do my university assignments in a faster way, so I could avoid the endless mouse clicks.
These days I use programming to automate routine System Administration on 1000's of Machines, monitor failure
and have fun orchestrating all these computers with simple and clean scripts.\textquotedblright
\end{small}\end{flushleft}
\end{minipage}
}
}
\end{changemargin}

\vspace*{-2.5mm}
\vspace{0.50cm}

\setlength\parindent{0pt}

\osection{Professional Experience}
\vspace{0.20cm}
\jobdes{System Engineer}{Science+Computing AG}{January 2011 - Current}
\vspace{0.20cm}
\begin{itemize}
 \item Install and Configure Windows and Linux (Red Hat 5,6 and CentOS) Workstations.
 \item Install and Configure HPC Clusters.
 \item Scripting: BASH, Python and Perl.
 \item Backup tool: TSM Client\textbackslash Server support (On Windows and Linux).
 \item Hardware and Software RAID configuration.
 \item Monitoring (Nagios\textbackslash RRDtool) Queuing systems (Sun Grid Engine\textbackslash In house queuing system written in Python).
 \item Windows\textbackslash Linux sharing (CIFS \& SAMBA).
 \item 2nd level support for Engineers using CAE\textbackslash CAD software.
 \item Install and configure MySQL databases.
 \item Install and configure SAN such as AutoFS and AMD.
 \item Maintain LDAP servers.
 \item Actively responsible for packaging software in RPM, DEB and other packaging format.
 \item Responsible for as much as 5000 computers (Workstations and cluster nodes) for renowned customers such Daimler, Porsche and BMW.
\end{itemize}
% Responsibilities included installation and configuration of Linux clusters and workstations, as well
% as Windows workstations; Support users of CAE\textbackslash CAD and Parallel computation software; 
% Backup solutions (IBM TIVOLY, Hardware and Software RAID configuration); Monitoring, Queuing systems,
% Windows\textbackslash Linux sharing (CIFS \& SAMBA); Python, BASH, Perl Scripting.
\par
\vspace{-0.3cm}
\hspace{0.2cm}
\foreach \x in {SAMBA, Red Hat, Windows, NFS, Python, Shell, MySQL, Perl} {%
    \tagf[My Tag Style]{\x}\hspace{-0.25cm}
}

\jobdes{Scientific Programmer }{Uni. British Columbia, Vancouver.}{May, 2010 - Oct., 2010}
\vspace{0.20cm}
\begin{itemize}
\item Implement a sequential version of a reactive transport model (Ground water flow + Chemical reactions) using an existing 
large and complex Fortran code. 
\item Write a collection of Python scripts: to submit jobs on different cluster hosts with different input files, 
to process the results and visualize them. 
\item The results of the code work and benchmarking comparing to previous versions
were submitted as M.Sc thesis.
\end{itemize}
\par
\vspace{-0.3cm}
\hspace{0.2cm}
\foreach \x in {Fortran95, Makefile, GCC, Python, \LaTeX} {%
    \tagf[My Tag Style]{\x}\hspace{-0.25cm}
}


\newpage
\jobdes{System Administrator, Python Programmer\hspace{1.0ex}}{Uni. Tübingen, Germany}{Oct. 2008-April 2010}
\\
\begin{itemize}
\item Install and configure home brewed 2 Debian clusters with 20 compute nodes.
\item Setup Subversion  \& Trac servers. 
\item Implement Python application to process GIS data and visualize the results (see blow MMSPy).
\item Maintain firewalls to the Clusters and the TRAC server. 
\end{itemize}
\par
\vspace{-0.3cm}\hspace{0.2cm}
\foreach \x in {Debian, Trac, Subversion, Python, GDAL, GIS, IPTables, PfSense} {%
    \tagf[My Tag Style]{\x}\hspace{-0.25cm}
    }

\jobdes{System Administrator}{Rankabove, Israel}{April, 2008 - August, 2008}
\\
\begin{itemize}
 \item Configuration management of Windows, OSX desktops and Ubuntu\textbackslash Debian Servers.
 \item Install and maintain Bugzilla for our clients.
 \item Package software (DEB format) for deployment.
\end{itemize}
\par
\vspace{-0.3cm}\hspace{0.2cm}
\foreach \x in {Debian, Packaging, Bugzilla, Ubuntu, Shell, Python, OSX, Windows} {%
    \tagf[My Tag Style]{\x}\hspace{-0.25cm}}

\osection{Education}
\vspace{0.7cm}
\jobdes{M. Sc. Applied Env. Geosciences}{Universität Tübingen, Germany}{October 2008 - October 2010}\vspace{0.2cm}
\\
{\bf Thesis Title:}\\{\em Implementation of Sequential Non Iterative approach in MIN3P reactive 
transport code and comparison of Global Implicit Method}, final GPA 1.6.

%\vspace{-.1cm}
% {\em Matlab Instructor} \hfill {\bf October, 2009 - February, 2010}\\
% Co-taught graduate level course for the Master of Applied Environmental Geosciences in
% Matlab Programming. Helped instructing student during classes.  
% \vspace*{.05in}  

% {\em Research Assistant, HiWi} \hfill {\bf October, 2008 - April, 2010}\\
% Support for Hydrogeology Work Group. Installed, configured and maintained 2 Linux Clusters used to perform 
% complex large scale watershed modeling. Supervisor: Dr. Claudius Bürger.\\
% Support for DSITE Work Group. Implemented a GIS application using MapServer, 
% Python and GDAL library. Supervisors: Dr. Michael Finkel, Dipl. Geol. Maximilian Morio.

% \vspace*{-.2cm}  

% {\bf Hebrew University}, Jerusalem, Israel \hfill {\bf October, 2007 - August, 2008}\\
% {\em M. Sc. Cand. Oceanography, Research Assistant}\\
% I have attended advanced courses in Oceanography, as well as practical field and lab
% work on $CO_2$ cycles and productivity and past climate changes.
% %  As a
% research assistant I was a part of team that studied biological calcification
% processes in the oceans, and used chemical proxies to deduce past climate changes.
\jobdes{B.Sc. Geology}{Hebrew University, Jerusalem}{October, 2003 - March, 2008}\\
{\em B.Sc. Final GPA 88/100.}\\
\vspace*{-.2cm}  

\osection{Computer Skills Summary}
\textbf{Programming Languages}:  Python, Matlab\textbackslash Octave, BASH, Perl, R, JAVA, \LaTeX, C and FORTRAN\\
\textbf{Applications}: git, Subversion, ArcGIS, QGIS, MapServer. \\
\textbf{Operating Systems}:   Red Hat\textbackslash Debian, *BSD, AIX, Windows, OSX\\
\textbf{Server Side Applications}: Apache, MySQL, SAMBA, Subversion, Trac, Apache, IBM Tivoli SM, NFS \& AutoFS,  
BIND, LDAP\textbackslash NIS.\\
\textbf{Configuration Management \& Monitoring}: Salt-Stack, Chef, Fabric, Nagios.
\osection{Open Source Projects}
\textbf{MMSPy}: Remediation and Planning Conflict analysis algorithm developed in Python using GDAL. \\
Libraries and tools used: Python, NumPy SciPy, Matplotlib, GDAL.
\texttt{https://github.com/oz123/mmspy}

\vspace*{-.2cm}  
\textbf{Pwman3}: Console based password management application \\
Libraries and tools used: Python, SQLite, MySQL.
\texttt{https://github.com/pwman3/pwman3}\\


\osection{Honors and Awards}
\$4000 U. of British Columbia, Department Earth Ocean Sciences, M. Sc. Research. \hfill \textbf{2010} \\
\$1000  Hebrew U., Prochter Foundation M. Sc. Research. \hfill \textbf{2008} \\
\$2000  Hebrew U., Academy-Community Partnership for Social Change. \hfill  \textbf{2007} \\
	   Honored Graduate of the Federman School of Public Policy.\hfill \textbf{2007} \\
	   Representative for  Intel Science and Engineering Fair (Detroit, MI, USA) \hfill \textbf{2000}\\
	   Representative for Israel, Europe's Young Scientists Fair (Thessaloniki, Greece) \hfill \textbf{1999}\\
	   $2^{nd}$ Place, Israel's Young Scientists Contest. \hfill \textbf{1999} \\
\vspace{-0.6cm}

\osection{Language Skills}

\begin{small}Mother language: Hebrew.\\

\vspace{-.3cm}  

\newcommand{\mc}[3]{\multicolumn{#1}{#2}{#3}}
% \begin{center}
\begin{tabular}{lllll}
 Other languages$^*$: & \mc{2}{c}{Understanding} & \mc{1}{c}{Speaking} & \mc{1}{c}{Writing}\\
  & Listening & Reading &  & \\
English & C2 & C2 & C2 & C2\\
German & C1 & C1 & C1 & B2
\end{tabular}
% \end{center}
\end{small}\\
\vspace{-.3cm}
\begin{footnotesize}$^*$ Evaluation according to Common European Framework of Reference (CEF). 
\end{footnotesize}

\osection{Driving License}
 PKW, Private Auto, Class B.

\osection{Work Permit}

Eligible to work and live in Germany and in Canada.
\end{resume}
\end{document}

